The Right Way to Search Evolving Graphs

### 2016-02-22 paper.tex
add book section

Although it is well known that sparse matrix-vector product is equivalent to a 
one-step BFS on the corresponding graph~\cite{kegi11},
it is little known about the generalization of this duality for evolving graphs.
In fact, previous works form the off-diagonal blocks wrongly~\cite{fehi15}. 
We prove the generalization of this duality by finding
the correct block sparse matrix representation of an evolving graph.
This work forms the basis for many algebraic evolving graph algorithms.

>>>>

Although it is well known that sparse matrix-vector product is equivalent to a 
one-step BFS on the corresponding graph~\cite[Sec. 1.1]{kegi11},
it is little known about the generalization of this duality for evolving graphs.
In fact, previous works form the off-diagonal blocks wrongly~\cite{fehi15}. 
We prove the generalization of this duality by finding
the correct block sparse matrix representation of an evolving graph.
This work forms the basis for many algebraic evolving graph algorithms.
